Efficiently summarising relationships in large samples: a general duality between statistics of genealogies and genomes

### 2019-09-13 treestats_paper.tex
Fix "this what"
remove old comment

\krt{There is another approach, introduced by Molly Prz.  I'll see if I can dig up a description.  The approach
described here is preferable, though.}

@@

Many genomic datasets only contain genotype information at a subset of sites
that do not represent an unbiased look at genome-wide variation,
introducing an ascertainment bias that difficulty for many applications.
If, however, unbiased tree sequences can be inferred using these data,
then Branch statistics could provide unbiased estimates of genome-wide quantities.
This is in principle possible, as \citet{kelleher2019inferring} inferred tree sequences
with UK BioBank data, produced using genotyping arrays \citep{bycroft2018genome}.
This would be similar to imputation, and would likely face similar challenges.

>>>>

@@

Many genomic datasets only contain genotype information at a subset of sites
that do not represent an unbiased look at genome-wide variation,
introducing an ascertainment bias that difficulty for many applications.
If, however, unbiased tree sequences can be inferred using these data,
then Branch statistics could provide unbiased estimates of genome-wide quantities.
This is in principle possible, as \citet{kelleher2019inferring} inferred tree sequences
with UK BioBank data, produced using genotyping arrays \citep{bycroft2018genome}.
This procedure would be similar to imputation, and would likely face similar challenges.
